WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-12-25 Thesis.tex
Proofread Chapter 4
Fix: NWM
Fixed: Bib IEEE style
Upgrade Future work
Proof read: Chapter 1

\usepackage{setspace}
\usepackage{tabu}
\usepackage[acronym,nopostdot,nonumberlist]{glossaries}
\makeglossaries
\usepackage{import}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{dirtytalk}
\usepackage{tabulary}
\usepackage{biblatex}
\usepackage[titletoc]{appendix}

\usepackage{color,soul}
\usepackage{todonotes}
\newcommand{\db}[1]{\textcolor{blue!40}{#1}}
\newcommand{\dbc}[1]{\todo[author=Dilum, inline, color=blue!40]{#1}}
\newcommand{\gkc}[1]{\todo[author=Gihan, inline, color=green!50]{#1}}

@@

        %\vfill
       \vspace{72pt}
        \large
        Department of Computer Science and Engineering\\
        \vspace{24pt}
        University of Moratuwa\\
        Sri Lanka\\
        \vspace{32pt}
        May 2020

@@

        Herath Mudiyanselage Gihan Chanuka Karunarathne\\
        \vspace{24pt}
       % \normalsize
        178008U\\
         \vspace{72pt}
        \normalsize
        Thesis submitted in partial fulfillment of the requirements for the degree Master of Science in Computer Science and Engineering\\

        %\vfill
       \vspace{72pt}
        \large
        Department of Computer Science and Engineering\\
        \vspace{24pt}
        University of Moratuwa\\
        Sri Lanka\\
        \vspace{32pt}
        May 2020

@@

\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before using such multimodal data in a NWM, it is necessary to transcode data into a format that can be ingested by the \acrshort{nwm}. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}. The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic and agricultural insurance firms.
Existing weather data integration systems are based on monolithic or client-server architectures; hence, unable to benefit from novel computational models such as cloud computing and containerized applications. Moreover, most of these software are proprietary or closed-source, making it difficult to customize them for an island like Sri Lanka with different weather seasons.
Therefore, in this research, we propose \acrfull{wdias} that utilizes modern architectural patterns such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing. The use of stateless microservices also enables \acrshort{wdias} to add new features on the fly with rollover capabilities. Moreover, \acrshort{wdias} provides a modular framework to integrate data from different sources, export into different formats, and add new functionality by adding extension modules.
We demonstrate the utility of \acrshort{wdias} using cloud-based experimental setup and weather-related synthetic workloads.

@@

\addcontentsline{toc}{chapter}{References}
\printbibliography[title={References}]

>>>>

\usepackage{setspace}
\usepackage{tabu}
\usepackage[acronym,nopostdot,nonumberlist]{glossaries}
\makeglossaries
\usepackage{import}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{dirtytalk}
\usepackage{tabulary}
\usepackage[style=ieee]{biblatex}
\usepackage[titletoc]{appendix}
\usepackage{siunitx}

\usepackage{color,soul}
\usepackage{todonotes}
\newcommand{\db}[1]{\textcolor{blue!40}{#1}}
\newcommand{\dbc}[1]{\todo[author=Dilum, inline, color=blue!40]{#1}}
\newcommand{\gkc}[1]{\todo[author=Gihan, inline, color=green!50]{#1}}
\newcommand{\gc}[1]{\todo[author=Gihan Revisit, inline, color=orange!50]{#1}}

@@

        %\vfill
       \vspace{72pt}
        \large
        Department of Computer Science and Engineering\\
        \vspace{24pt}
        University of Moratuwa\\
        Sri Lanka\\
        \vspace{32pt}
        August 2020

@@

        Herath Mudiyanselage Gihan Chanuka Karunarathne\\
        \vspace{24pt}
       % \normalsize
        178004U\\
         \vspace{72pt}
        \normalsize
        Thesis submitted in partial fulfillment of the requirements for the degree Master of Science in Computer Science and Engineering\\

        %\vfill
       \vspace{72pt}
        \large
        Department of Computer Science and Engineering\\
        \vspace{24pt}
        University of Moratuwa\\
        Sri Lanka\\
        \vspace{32pt}
        August 2020

@@

\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format that can be ingested by the \acrshort{nwm}. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}. The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic and agricultural insurance firms.
Existing weather data integration systems are based on monolithic or client-server architectures; hence, unable to benefit from novel computational models such as cloud computing and containerized applications. Moreover, most of these software are proprietary or closed-source, making it difficult to customize them for an island like Sri Lanka with different weather seasons.
Therefore, in this research, we propose \acrfull{wdias} that utilizes modern architectural patterns such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing. The use of stateless microservices also enables \acrshort{wdias} to add new features on the fly with rollover capabilities. Moreover, \acrshort{wdias} provides a modular framework to integrate data from different sources, export into different formats, and add new functionality by adding extension modules.
We demonstrate the utility of \acrshort{wdias} using cloud-based experimental setup and weather-related synthetic workloads.

@@

\addcontentsline{toc}{chapter}{References}
\renewcommand*{\UrlFont}{\rmfamily}
\printbibliography[title={References}]

### 2020-12-25 introduction/sec_1-motivation.tex
Fixed: Bib IEEE style
Proof read: Chapter 1

\acrfull{curw} \cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka. \acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability rather than depending on existing weather data integration systems. \acrshort{curw} collects real-time data from weather stations and other relevant entities and generates daily forecasts. Then the generated results are shared with relevant public departments responsible for disaster planning, risks mitigation, and disaster management. One of the future goals of \acrshort{curw} is to open up data to the public enabling both societal and commercial use cases.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
To enhance the accuracy of weather forecast, it is necessary to provide reliable and detailed weather data as inputs to \acrshort{nwm}. These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective NWMs, it is necessary to convert them to a data format that can be ingest by the models. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.

Weather data processed by a NWM maybe used by several other \acrshort{nwm}, as well as by many third-party applications and researcher. For example, logistic companies could use the processed data with their data models to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers, as well as calculate premiums based on the anticipated weather patterns. Besides, farmers could rely on weather forecasts to plan their work.

Data Integration and Analysis System (DIAS) \cite{Kawasaki2018DataReduction} and Meteorological Assimilation Data Ingest System (MADIS) \cite{Macdermaid2005ArchitectureP2.39} are two of the well-known Weather Data Integration and Assimilation (WDIA) systems. However, those are proprietary systems. Further, while \acrfull{fews} \cite{Werner2013TheSystem} is free to use, but it is not open source. While a few other data integration systems exists, most of them are also proprietary or closed source. Thus, it is difficult and costly to customize such systems for an island like Sri Lanka which experience different kinds of weather seasons over the year \cite{NaveendrakumarFiveLanka}.
For example, \acrshort{fews} does not support FLO2D model integration, which is used by \acrshort{curw} to forecast water level.

Existing WDIA systems are based on the monolithic or client service architecture; hence, cannot benefit from technologies such as cloud computing to achieve high scalability and availability. Moreover, such systems cannot be updated or reconfigured without taking the system off line. Furthermore, these systems are platform specific. For example, while \acrshort{fews} can run on either Windows or Linux, downtime is needed to introduce any changes to the system.

Given the above reasons, there is a necessity to develop a WDIA system that could handle large volumes of multimodel data efficiently while providing scalability and high throughput. Moreover, it is desirable to support controlled data sharing with other NWMs and third-party access to enable multiple use cases. Furthermore, such a system should be architectured to benefit from technologies such as cloud computing and microservices.

>>>>

\acrfull{curw} \cite{CUrWSL2017Lanka} is tasked with the mission to reduce water-related natural disasters in Sri Lanka. \acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability rather than depending on existing weather data integration systems. \gkc{Because of existing weather systems are not open source to configure as required, and not flexible enough to change without much help from the maintainers.} \acrshort{curw} collects real-time data from weather stations and other relevant entities and generates daily forecasts. Then the generated results are shared with relevant public departments responsible for disaster planning, risks mitigation, and disaster management. One of the future goals of \acrshort{curw} is to open up data to the public enabling both societal and commercial use cases.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
To enhance the accuracy of weather forecast, it is necessary to provide reliable and detailed weather data as inputs to \acrshort{nwm}. These \acrshort{nwm}s utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective \acrshort{nwm}s, it is necessary to convert them to a data format that can be ingest by the models. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwm}s.

Weather data processed by a \acrshort{nwm} maybe used by several other \acrshort{nwm}, as well as by many third-party applications and researcher. For example, logistic companies could use the processed data with their data models to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers, as well as calculate premiums based on the anticipated weather patterns. Besides, farmers could rely on weather forecasts to plan their work.

\acrfull{dias} \cite{Kawasaki2018DataReduction} and \acrfull{madis} \cite{Macdermaid2005ArchitectureP2.39} are two of the well-known Weather Data Integration and Assimilation (WDIA) systems. However, those are proprietary systems. Further, while \acrfull{fews} \cite{Werner2013TheSystem} is free to use, but it is not open source. While a few other data integration systems exists, most of them are also proprietary or closed source. Thus, it is difficult and costly to customize such systems for an island like Sri Lanka which experience different kinds of weather seasons over the year \cite{NaveendrakumarFiveLanka}.
For example, \acrshort{fews} does not support FLO2D model integration, which is used by \acrshort{curw} to forecast water level.

\gc{To address such issues, there is a parallel researches also try to implement an open-data open-model framework called as Meta Scientific Modeling (MSM).} But the existing WDIA systems and emerging systems are also based on the monolithic or client service architecture; hence, cannot benefit from technologies such as cloud computing to achieve high scalability and availability. Moreover, such systems cannot be updated or reconfigured without taking the system off line. Furthermore, these systems are platform specific. For example, while \acrshort{fews} can run on either Windows or Linux, downtime is needed to introduce any changes to the system.

Given the above reasons, there is a necessity to develop a WDIA system that could handle large volumes of multimodel data efficiently while providing scalability and high throughput. Moreover, it is desirable to support controlled data sharing with other NWMs and third-party access to enable multiple use cases. Furthermore, such a system should be architectured to benefit from technologies such as cloud computing, microservices, and loosely coupled containerized applications.

### 2020-12-25 introduction/sec_2-problem_and_objectives.tex
v5.2.2 Intro
Upgrade Future work
Proof read: Chapter 1

\section{Problem Statement}
Handling spatio-temporal weather data is challenging, as it involves large data volumes requiring high computing, storage, and network resources. Moreover, the data integration system needs to be capable of interacting with different data formats including spatio-temporal bulk stream data. Furthermore, it should support geographical and time-based queries, as well as provide third-party access to data with easy integration. Scalability and high availability are also essential to support different use cases and mission-critical nature of applications.
Further, users should be able to easily deploy and manage the system while benefiting from technological advances. 
In this context, the research problem can be stated as follows:

@@

\section{Objectives}
This research addresses the above problem statement by achieving the following research objectives:
\begin{itemize}
    \item To develop a platform to integrate weather data from different sources in different formats
    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage
    \item To optimize data schema to support geospatial and time-based queries
    \item To develop an API for third-party data sharing
    \item To perform a load test to analyse throughput, scalability of the system
\end{itemize}

>>>>

\section{Problem Statement}
Handling spatio-temporal weather data is challenging, as it involves large data volumes requiring high computing, storage, and network resources. Moreover, the data integration system needs to be capable of interacting with different data formats including spatio-temporal bulk stream data. Furthermore, it should support geographical and time-based queries, as well as provide third-party access to data with easy integration. Scalability and high availability are also essential to support different use cases and mission-critical nature of applications.
Further, users should be able to easily deploy and manage the system while benefiting from technological advancements. 
In this context, the research problem can be stated as follows:

@@

\section{Objectives}
This research addresses the above problem statement by achieving the following research objectives:
\begin{itemize}
    \item To develop a platform to integrate weather data from different sources in different formats
    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage
    \item To optimize data schema to support geospatial and time-based queries
    \item To develop an API for third-party data sharing
    \item To efficiently utilize cloud computing infrastructure with low-cost
\end{itemize}

### 2020-12-25 introduction/sec_3-outline.tex
Done scan reading
Proof read: Chapter 1

\section{Outline}
The organization of the rest of the thesis is as follows; In \cref{ch:literature} the literature review is presented. It discusses the existing weather data integration systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}. Solution approach including the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}. It provides details on how the \acrshort{wdias} is designed by following a microservice architecture and its data pre-processing capabilities. Performance analysis is presented in Chapter \ref{ch:results}. Here we discuss the experimental setup of the \acrshort{wdias} and analyze the observations concerning performance metrics. Finally, Chapter \ref{ch:summary}, summarizes the research work and further discusses the research limitations and future work.

>>>>

\section{Outline}
The organization of the rest of the thesis is as follows; In \cref{ch:literature}, the literature review is presented. It discusses the existing weather data integration systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, \acrshort{dias}, and \acrshort{msm}. Solution approach including the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}. It provides details on how the \acrshort{wdias} is designed by following a microservice architecture and its data pre-processing capabilities. Performance analysis is presented in Chapter \ref{ch:results}. Here we discuss the experimental setup of the \acrshort{wdias} and analyze the observations concerning performance metrics. Finally, Chapter \ref{ch:summary}, summarizes the research work and further discusses the research limitations and future work.
